%Acknowledgments

\renewcommand{\baselinestretch}{2}
\small\normalsize
\hbox{\ }

\vspace{-.65in}

\begin{center}
\large{Acknowledgments}
\end{center}

\vspace{1ex}

I have been truly fortunate to know and work with many outstanding people throughout my career, and I am grateful to all of you.

First and foremost, I would like to thank my advisor Mihai Pop.
It has been an absolute privilege to be under your guidance for the past 8 years.
You were the first person in my life that I would consider my role model.
I am eternally greatful for the advice, support, and encouragement you gave me and hope to pay it forward someday.

I would also like to thank all of my other committee members. I will always enjoy the [often off-topic] discussions with Atif Memon who has introduced me to the world of software testing.
I am in indebted to H\'{e}ctor Corrado Bravo for increasing the focus of statistics within the Center for Bioinformatics and Computational Biology.
I wish to thank Michael Cummings for his mentorship and allowing me to work abroad with him.
I have built up collabrations and friendships that were made possible thanks to him.
I am also very grateful to Stephen Mount for always being able to answer any biological question I come up with during our social hours.

I owe a great deal of thanks to countless past and present faculty and graduate students at the University of Maryland.
In particular, the majority of this dissertation was only made possible with the help of MohammadReza Ghodsi, Irina Astrovskaya, and Henry Lin.
In addition, I owe a great deal of thanks to Sergey Koren who has been my mentor and oracle for all things related to assembly.
Ted Gibbons would always listen to me rant about negative results and lack of progress.
I would also like to thank everyone (past and present) from the labs of Mihai Pop, H\'{e}ctor Corrado Bravo, Sridhar Hannenhali, and Steven Salzberg.

Finally, I must thank my friends and family who have supported and loved me unconditionally throughout this adventure.

It is impossible to remember everyone, so I apologize to anyone who may have been left out. If I forgot you, let me know and I will happily by you a drink.
