%Preface

\renewcommand{\baselinestretch}{2}
\small\normalsize
\hbox{\ }

\vspace{-.65in}

\begin{center}
\large{Preface}
\end{center}


The algorithms, software, and results in this dissertation have either been published in peer-reviewed journals and conferences or are currently under preparation for submission.
At the time of this writing, Chapters 2, 3, 4, and 6 have already been published or submitted and are reformatted here. Chapter 5 is under preparation for submission.
I am indebted to my co-authors on these projects - their dedication and knowledge in the areas of computer science, statistics, and biology have resulted in much stronger scientific papers. \\

\noindent\textbf{Chapter 2}:

\noindent - Mohammadreza Ghodsi*, Christopher M. Hill*, Irina Astrovskaya, Henry Lin, Dan D. Sommer, Sergey Koren, and Mihai  Pop. \textit{De novo likelihood-based measures for comparing genome assemblies}. BMC research notes 6, no. 1 (2013): 334.

The authors would like to thank H\'{e}ctor Corrada Bravo and Bo Liu for their advice on the sampling procedure and associated statistics, Todd Treangen for advice on accessing the GAGE data, and the other members of the Pop lab for valuable discussions on all aspects of our work. This work was supported in part by the National Science Foundation
(grants IIS-0812111, IIS-1117247 to MP), and by the National
Institutes of Health (grant R01-HG-004885 to MP).\\

\noindent\textbf{Chapter 3}:

\noindent - Christopher M. Hill, Irina Astrovskaya, Heng Huang, Sergey Koren, Atif Memon, Todd J. Treangen, and Mihaela Pop. \textit{De novo likelihood-based measures for comparing metagenomic assemblies}. In Bioinformatics and Biomedicine (BIBM), 2013 IEEE International Conference on, pp. 94-98. IEEE, 2013.

The authors would like to thank the members of the Pop lab for valuable discussions on all aspects of our work. This work was supported in part by the NIH, grant R01-AI-100947 to MP, and the NSF, grant IIS-1117247 to MP. \\

\noindent - Koren, Sergey, Todd J. Treangen, Christopher M. Hill, Mihai Pop, and Adam M. Phillippy. \textit{Automated ensemble assembly and validation of microbial genomes}. BMC bioinformatics 15, no. 1 (2014): 126.

The authors would like to thank Magoc et al. and Comas et al. who submitted the raw data that was used in this study. We thank Lex Nederbragt and an anonymous reviewer for detailed comments on the manuscript and iMetAMOS software, usability, and documentation.  MP and CMH were supported by NIH grant R01-AI-100947and the NSF grant IIS-1117247. \\

\noindent\textbf{Chapter 4}:

\noindent - Christopher M. Hill, Sergey Koren, Daniel Sommer, Bryan Dzung Ta, Atif Memon. and Mihai Pop. \textit{\emph{De novo} genome assembly regression testing}. Under revision.

The authors would like to thank members of the Memon and Pop labs for their support and valuable discussions. This work was supported by NIH grant R01-AI-100947 to MP. \\

\noindent\textbf{Chapter 5}:

\noindent - Christopher M. Hill, Jonathan Gluck, Atif Memon, and Mihai Pop. \textit{VALET: a \emph{de novo} pipeline for finding metagenomic mis-assemblies}. In preparation. \\

\noindent\textbf{Chapter 6}:

\noindent - Christopher M. Hill, Carl H. Albach, Sebastian G. Angel, and Mihai Pop. \textit{K-mulus: Strategies for BLAST in the Cloud}. In Parallel Processing and Applied Mathematics, pp. 237-246. Springer Berlin Heidelberg, 2014.

The authors would like to thank Mohammadreza Ghodsi for advice on clustering, Daniel Sommer for advice on Hadoop, Lee Mendelowitz for manuscript feedback, Katherine Fenstermacher for the name K-mulus, and the other members of the Pop lab for valuable discussions on all aspects of our work. \\

\noindent - Christopher M. Hill, Andras Szolek, Mohamed El Hadidi, and Michael Cummings. \textit{Lossy compression of DNA sequencing quality data}. Under review.

The authors would like to thank the 2014 Bioinformatics
Exchange for Students and Teachers (\textsc{best}) Summer School,
funded by the offices of the Dean of The Graduate School at University
of Maryland and the Rektor of University of T\"{u}bingen, where this
research was initiated.
